% Assumes ifthen package
% Defines 3 commands that correspond to boolean values
%   1. \confposter        :  USE_CONFERENCE_POSTER                :  conference posters
%   2. \confpresentation  :  USE_CONFERENCE_PRESENTATION          :  conference talks
%   3. \confinvited       :  USE_CONFERENCE_INVITED_PRESENTATION  :  conference invited talks
% Each command will create a new item (in an itemized environment) and spit out the text if the corresponding boolean flag is enabled.

\newcommand{\confposter}[1]{\ifthenelse{\boolean{USE_CONFERENCE_POSTER}}{\item #1}{}}
\newcommand{\confpresentation}[1]{\ifthenelse{\boolean{USE_CONFERENCE_PRESENTATION}}{\item #1}{}}
\newcommand{\confinvited}[1]{\ifthenelse{\boolean{USE_CONFERENCE_INVITED_PRESENTATION}}{\item Invited: #1}{}}

% TODO: try to use bibliographic files here.
% Formatting:
% <Authors>
% <(Year, Month)>
% <Title>
% <Name of conference>,
% <Location>

\begin{itemize*}
% All presentations here should be ones that /I/ presented.
% TODO: Submitted/accepted?
% TODO: workshops? TMS 2018, CALPHAD 2018, CALPHAD 2019, CALPHAD 2020, IMAT 2020

% TMS 2020
\confpresentation {
\textbf{B. Bocklund*}, R.A. Otis, Z.-K. Liu
(2020, February).
Uncertainty quantification and propagation in ICME enabled by ESPEI.
TMS 2020 Annual Meeting,
San Diego, CA.
}



% MS&T 2019
\confinvited {
\textbf{B. Bocklund*}, R.A. Otis, Z.-K. Liu
(2019, October).
Automated CALPHAD modeling and uncertanty quantification of a ternary system using ESPEI.
Materials Science and Technology 2019,
Portland, OR.
}

% CALPHAD 2019, Noah's talk that I gave
\confpresentation {
N.H. Paulson, \textbf{B. Bocklund*}, R.A. Otis, Z.-K. Liu, M. Stan
(2019, June).
Quantified Uncertainty in CALPHAD for Materials Design.
CALPHAD XLVIII,
Singapore.
}

% CALPHAD 2019, Matt's poster
\confposter {
M. Feurer, \textbf{B. Bocklund*}, S. Shang, A. Beese, Z.-K. Liu
(2019, June).
High-Throughput Modeling of Cr-Fe-Ni Sigma Phase.
CALPHAD XLVIII,
Singapore.
}

% CALPHAD 2019, my poster
\confposter {
\textbf{B. Bocklund*}, R.A. Otis, Z.-K. Liu
(2019, June).
Automated CALPHAD modeling and uncertanty quantification of a ternary system using ESPEI.
CALPHAD XLVIII,
Singapore.
}

% TMS 2019
\confpresentation{
\textbf{B. Bocklund*}, L.D. Bobbio, R.A. Otis, S. Shang, A.M. Beese, Z.-K. Liu
(2019, March).
Impact of Uncertainty Quantification in Automated Calphad Modeling on the design of Additively Manufactured, Functionally-graded Alloys.
TMS 2019 Annual Meeting,
Phoenix, AZ.
}

% MS&T 2018
\confpresentation {
\textbf{B. Bocklund*}, R.A. Otis, Z.-K. Liu
(2018, October).
Computational Tools for the Automated Development of a Cr-Fe-Ni-Ti-V CALHPAD Database.
Materials Science and Technology 2018,
Columbus, OH.
}

% CALPHAD 2018
\confpresentation{
\textbf{B. Bocklund*}, A. Egorov, A. Obaied, R.A. Otis, I. Roslayakova, Z.-K. Liu
(2018, May).
ESPEI for Efficient Database Development, Modification and Uncertainty Quantification.
CALPHAD XLVII,
Juriquilla, Mexico.
}


% TMS 2018
\confpresentation{
\textbf{B. Bocklund*}, R.A. Otis, Z.-K. Liu
(2018, March).
Thermodynamic Modeling with Uncertainty Quantifiation and its Implicitaions for Additive Manufacturing.
TMS 2018 Annual Meeting,
Phoenix, AZ.
}

% ICME 2017
\confposter{
\textbf{B. Bocklund*}, R.A. Otis, J. Paz Soldan-Palma, Y. Wang, Z.-K. Liu
(2017, May).
Automating Thermodynamic Database Development with ESPEI.
4th World Congress on Integrated Computational Materials Engineering,
Ypsilanti, MI.
}
\end{itemize*}


\vspace{-0.6em}
\hspace{0.5em}{\small \emph{\textbf{*} presenter}}
\vspace{0.4em}
